---
title: "p8105_hw3_hq2182"
author: "Hanfei Qi"
date: "10/6/2020"
output: html_document
---

# Problem 1

```{r, message = FALSE, warning = FALSE}
library(p8105.datasets)
library(tidyverse)
data("instacart")
```

This dataset contains `r nrow(instacart)` rows and `r ncol(instacart)` columns.

Observations are the level of items in orders by user. There are user / order variables -- user ID, order ID, order day, and order hour. THere are also item variables -- name, aisle, department, and some numeric codes. -----------(need to be revise)-------------

How many aisles, and which are mroe items from?

```{r}
instacart %>%
  count(aisle) %>%
  arrange(desc(n))
```

Make a plot

```{r}
instacart %>%
  count(aisle) %>% 
  filter(n > 10000) %>% 
  mutate(
    aisle = factor(aisle),
```


```{r}
aisle = fct_reorder(aisle, n)
  ) %>% 
  ggplot(aes(x = aisle, y = n)) +
  geom_point() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

Make a table

```{r}
instacart %>% 
  filter(aisle %in% c("baking ingredients", "dog food care", "packaged vegetables fruits")) %>%
  group_by(aisle) %>% 
  count(product_name) %>% 
  mutate(rank = min_rank(desc(n))) %>% 
  filter(rank < 4) %>% 
  arrange(aisle, rank) %>% 
  knitr::kable()
```

Apples vs. ice cream

```{r}
instacart %>% 
  filter(product_name %in% c("Pink Lady Apples", "Coffee Ice Cream")) %>% 
  group_by(product_name, order_dow) %>% 
  summarize(mean_hour = mean(order_hour_of_day)) %>% 
  pivot_wider(
    names_from = order_dow,
    values_from = mean_hour
  )
```

